---
title: "Forecast_Stock"
author: "Nandhini K Mohan"
date: "02/05/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Loading Libraries
```{r}
library(quantmod)
library(tseries)
library(timeSeries)
library(forecast)
library(xts)
```

#Fetching TMobile data from Yahoo Finance
```{r}
tmus_data <- getSymbols(Symbols = "TMUS", src = "yahoo", from = '2021-05-02', 
        to = Sys.Date(), auto.assign = FALSE)
head(tmus_data)
```

#Taking the 4th column i.e., Close price into separate dataframe
```{r}
close_price <- tmus_data[,4]
head(close_price)
```

#Calculating log return
```{r}
log_return <- diff(log(close_price), lag=1)
log_return <- log_return[!is.na(log_return)]
head(log_return)
```

#Plotting the graph of log return
```{r}
plot(log_return, type='l', main='log return plot')
```

#ADF Test on log_return to check for stationarity
```{r}
print(adf.test(log_return))
```

#Splitting the dataset into train data and test data
```{r}
breakpoint = floor(nrow(log_return)*(2.9/3))
head(breakpoint)
```

#Plotting ACF and PACF - Deciding p,q values of Arima
```{r}
par(mfrow= c(1,1))
acf.log_return = acf(log_return[c(1:breakpoint),], main='ACF Plot', lag.max = 100)

pacf.log_return = pacf(log_return[c(1:breakpoint),], main='PACF Plot', lag.max = 100)
```

#Actual series
```{r}
Actual = xts(0, as.Date("2022-01-01", "%Y-%m-%d"))
Actual
```
#Forecasted series
```{r}
forecasted_series = data.frame(Forecasted=numeric())

for(b in breakpoint:(nrow(log_return)-1))
{
train_data = log_return[1:b,]
test_data = log_return[(b+1):nrow(log_return),]

#Arima model of (2,0,2)

fit = arima(train_data, order=c(2,0,2), include.mean = FALSE)
summary(fit)

acf(fit$residuals, main="Residual Plot")

arima.forecast = forecast(fit, h=1, level=99)
summary(arima.forecast)

par(mfrow=c(1,1))
plot(arima.forecast, main="Arima Forecast")

forecasted_series = rbind(forecasted_series, arima.forecast$mean[1])
colnames(forecasted_series)=c("Forecasted")

Actual_return = log_return[(b+1),]
Actual = c(Actual, xts(Actual_return))
rm(Actual_return)

print(close_price[(b+1),])
print(close_price[(b+2),])
}
```

#Adjusting the length of Actual series
```{r}
Actual = Actual[-1]
```

#Time series object of the forecast
```{r}
forecasted_series = xts(forecasted_series, index(Actual))
```

#Plotting Actual vs Forecasted returns
```{r}
par(mar = c(1, 1, 1, 1))
plot(Actual, type='l', main='Actual Returns')
lines(forecasted_series, lwd=1.5, col='red')
#legend('bottomright', c("Actual", "Forecasted"), lty=c(1,1), lwd=c(1.5,1.5), col=c('black', 'red'))

legend('bottomright', legend=c("Actual", "Forecasted-1"), lty=c(1,1), lwd=c(1.5,1.5), col = c("blue","red"))
```

#Accuracy of the forecast
```{r}
comparison = merge(Actual, forecasted_series)
comparison$Accuracy = sign(comparison$Actual) == sign(comparison$Forecasted)
print(comparison)
```

#Computing the Accuracy percentage
```{r}
Accuracy_percentage_1 = sum(comparison$Accuracy ==1)*100/length(comparison$Accuracy)
print(paste("Accuracy Percentage using the model (2,0,2): " ,Accuracy_percentage_1))
```

